Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-28 parts/sa.tex
fix PrioCont
new formalism: simultaneously required processes

Processus rencontrés :
\begin{align*}
&\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, p \in ps \\
  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
\end{align*}

@@

\subsection{Abstract structure}
%Séquences de bonds abstraites :
%$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
%where:
%$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $\cwB = \sfp{\aB^\w_{\update(\ctx)}}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
%%% Version états stables locaux
%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

>>>>

Processus rencontrés :
\todo{Revenir à la définition simple de procs ?}
\begin{align*}
&\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, p \in ps \\
  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
\end{align*}

@@

\subsection{Abstract structure}

@@

\begin{definition}[$\csState$]
  \label{def:csState}
  \towrite{À reformuler}
  $$\csState(a_i) = \{ b_j \in \PHproc \mid b \in \Vs(a) \wedge \pfp_{\csState(a_i)}(a) = a_i \}$$
\end{definition}

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) = \towrite{\in?} ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}

\begin{definition}[Coherent solution]\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\myrsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\myreq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}

\begin{theorem}[Approximation inf.]\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all cooperative sort requisites are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

\begin{proof}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.

\towrite{MQ par récurrence : tous les $a_i$ requis de sortes coopératives sont concrétisables}

As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
      \begin{itemize}
        \item[*] \towrite{construire récurvivement ? Distinguer les cas $b_j$ dans $\components$ ou $\cs$ (stabilité requise et obtenue)}
        For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

%%% Ancien graphe avec PrioCont
\begin{comment}
\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $\cwB = \sfp{\aB^\w_{\update(\ctx)}}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      \exists (a_i, \PHobj{a_j}{a_i}) \in \myreq\\
      & \qquad\qquad \wedge a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
%%% Version états stables locaux
%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
\end{proof}
\end{comment}
